Viral Sequence Sorting Tools Evaluation

### 2022-09-09 TestingPipeline/Scripts/rule_tuning_2022.09.06.Rmd
Experimenting with new DVF rules accounting for length.

  if (include_deepvirfinder) {
    keep_score[input_seqs$score>=0.7] <- keep_score[input_seqs$score>=0.7] + 0.5
#   keep_score[input_seqs$score>=0.9] <- keep_score[input_seqs$score>=0.9] + 0.5
  }

@@

## Visualize how the precision, recall, and F1 scores change across pipelines.
```{r}
pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")

p2 <- ggplot(accuracy_scores, aes(x=toolcombo, y=F1)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("F1 Score")

p2

ggplot(accuracy_scores, aes(x=toolcombo, y=precision)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Precision")

ggplot(accuracy_scores, aes(x=toolcombo, y=recall)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Recall")
```

>>>>

  if (include_deepvirfinder) {
    keep_score[input_seqs$score>=0.7 & input_seqs$contig_length<10000] <- keep_score[input_seqs$score>=0.7 & input_seqs$contig_length<10000] + 0.5
   keep_score[input_seqs$score>=0.9 & input_seqs$contig_length<10000] <- keep_score[input_seqs$score>=0.9 & input_seqs$contig_length<10000] + 1
  }

@@

```{r}
library("stringr")
```

```{r}
accuracy_scores$numtools <- str_count(accuracy_scores$toolcombo, "1")
accuracy_scores <- accuracy_scores[order(accuracy_scores$numtools, decreasing=F),]
accuracy_scores$toolcombo <- factor(accuracy_scores$toolcombo, levels = unique(accuracy_scores$toolcombo))
accuracy_scores$numtools <- as.factor(accuracy_scores$numtools)
```

## Visualize how the precision, recall, and F1 scores change across pipelines.
```{r}
pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")
p2 <- ggplot(accuracy_scores, aes(x=toolcombo, y=F1, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("F1 Score")
p2
ggplot(accuracy_scores, aes(x=toolcombo, y=precision)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Precision")
ggplot(accuracy_scores, aes(x=toolcombo, y=recall)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (CV, DVF, KJ, VB, VS, VS2)") +
  ylab("Recall")
```
